Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-11-18 paper-webserver.tex
ADD: new paragraph on group comparison in Functionality

% group comparisons
By retrieving results from the database, Spfy provides group comparisons using Fishers.
...

% Panpredic???

>>>>

% group comparisons
Knowledge graphs are a semantic method of linking data points by their relations. Spfy allows users to compare the results associated with particular genome types or metadata by storing all results in a graph structure. Comparisons can be made in real-time, as new genomes are submitted for analysis and the results stored in the existing graph. Any data type in the graph is valid for analysis, such as the presence or absence of pan-genome regions against determined serotypes or other subtyping options. In addition, Spfy supports the submission of user-specified metadata, such as location or source information.
